Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-05-29 Paper.tex
tweaks

For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added. The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}. To complement the HTML, a CSS stylesheet is added which adds the some design elements. The design of the template is based on a presentation by S. Wolf \cite{Wolf:npentrel15}. To bring the presentation to life the library impress.js is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh. An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.

@@

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-1em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

@@

\begin{wrapfigure}r{.6\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-1em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-1em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
  \vspace{-.5em}
  \caption[Caption for LOF]{Visualization\footnotemark of Dependencies and Levels at
    60\degree}
  \label{fig:visualDependencyDegree}
\vspace{-1em}
\end{wrapfigure}
If Annie, while browsing through the different dependencies, realizes that she needs to
refresh her memory or learn more about any of the dependent information she can enter the
respective level. The presentation will then continue on that level and show all the
slides from that topic in the correct order. Once Annie has gone through this short
excursion, she can return to the initial slide and resume the primary narrative path. By
adding a way to explore these other levels, the presentation adds more context and allows
Annie to understand the subject on a deeper level. These modular excursions are included
in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
story line (see \autoref{fig:visualDependencyDegree}).

\footnotetext{The overlapping slides do not interfere as they are at a 90\degree\
  angle. Therefore when seeing one slide, the other slide will be visible only from the
  side. Since a slide is very thin this makes it invisible.}

@@

The most interesting movement is the rotations which aim to give the viewer the feeling of
entering a topic and a different storyline. Thus entering a different topic comes with a
change of perspective which is underlined by the 3D transformation that the user
sees. Overall, these movements add expressiveness to the relations and allow for intuitive
interaction with the presentation. \footnote{To see the presentation in action visit:
  \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}

>>>>

For including the XHTML or the PNGs we use self-created boilerplate code, in which only
some coordinates and the XHTML or the PNGs for the slide are added. The details of this
process will be explained in Section \ref{sec:narrativePaths},
\ref{sec:orderedInfoGraphs}, and \ref{sec:levels}. To complement the HTML, a CSS
stylesheet is added which adds the some design elements. The design of the template is
based on a presentation by S. Wolf \cite{Wolf:npentrel15}. To bring the presentation to
life the library impress.js is used because it makes it simple to reuse the XHTML code
that was automatically generated by lmh. An important additional reason for the choice of
impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative.

@@

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-2em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

@@

\begin{wrapfigure}r{.63\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-1em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-2em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
  \vspace{-.5em}
  \caption{Visualization of Dependencies and Levels at 60\degree}
  \label{fig:visualDependencyDegree}
\vspace{-1em}
\end{wrapfigure}
If Annie, while browsing through the different dependencies, realizes that she needs to
refresh her memory or learn more about any of the dependent information she can enter the
respective level. The presentation will then continue on that level and show all the
slides from that topic in the correct order. Once Annie has gone through this short
excursion, she can return to the initial slide and resume the primary narrative path. By
adding a way to explore these other levels, the presentation adds more context and allows
Annie to understand the subject on a deeper level. These modular excursions are included
in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
story line -- see \autoref{fig:visualDependencyDegree}. The overlapping slides do not
interfere as they are at a 90\degree\ angle. Therefore when seeing one slide, the other
slide will be visible only from the side. Since a slide is very thin this makes it
invisible.

@@

The most interesting movement is the rotations which aim to give the viewer the feeling of
entering a topic and a different storyline. Thus entering a different topic comes with a
change of perspective which is underlined by the 3D transformation that the user
sees. Overall, these movements add expressiveness to the relations and allow for intuitive
interaction with the presentation. The presentation can be found at
\url{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.
